---
title: "SafeVir_DIO_merged_figures alpha + beta"
output:
  pdf_document: default
  html_document:
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=F}
#Set working directory to script directory
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

#Load and prepare OTU-tables + color scale etc.
source("Analysis0_file_loading_and_prep.R")
```

# Alpha diversity

## By Treatment

```{r, eval = T, include = T, echo = F, message = F, warning=FALSE}

#Normalize to mean read count
standf = function(x, t=total) round(t * (x / sum(x)))
total = median(sample_sums(PSB))
PSB.R = transform_sample_counts(PSB, standf)

#Set desired alpha diversity metrics

alpha_met <- c("Shannon")



###########Boxplots

##Time

variable <- c("Treatment")
#Set sign argumetns
#symnum.args <- list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), symbols = c("****", "***", "**", "*", "ns"))
#my_comparisons = list( c("CP_CV", "CP_FVT"), c("CP_CV", "LGG_FVT"), c("CP_CV", "AM_FVT"), c("CP_CV", "LGG_CV"), c("CP_CV", "AM_CV"), c("AM_FVT", "AM_CV"), c("LGG_FVT", "LGG_CV") ) #All comparisons


alpha.Treatment <- plot_richness(PSB.R, measures=alpha_met , x=variable, color=variable) + 
  geom_boxplot(alpha=0.1, lwd = 1) +
  #stat_compare_means(comparisons = my_comparisons, method = "kruskal", paired = FALSE, symnum.args = symnum.args) +
  scale_color_jco() +
  theme_classic() +
  theme(text = element_text(size = 8),
        axis.line=element_line(size=1),
        axis.text=element_text(size = 8, colour = "Black"),
        axis.ticks=element_line(size=1, colour = "Black"),
        strip.background = element_rect(colour = "white", fill = "white"),
        axis.text.x=element_text(angle = 45, hjust = 1),
        strip.text.x = element_text(size = 10, angle = 0, face="bold"),
        legend.text = element_text(size = 8),
        legend.position = "none"
  ) +
  labs(x="Treatment",
       y="Alpha diversity")+
  facet_wrap("Sample_time_point")

alpha.Treatment
```

# Beta diversity

## Treatment

```{r, eval = T, include = T, echo = F, message = F}
#Do PCoA ordination based on Bray-curtis distance
GP.ord <- ordinate(subset_samples(PSB.CSS,Treatment != "NA"), "PCoA", "bray")

beta.treatment = phyloseq::plot_ordination(subset_samples(PSB.CSS,Treatment != "NA"), GP.ord, color="Treatment") + 
  stat_ellipse(geom = "polygon", level = 0.95, fill = NA, size = 1) +
  scale_color_jco() +
  theme_classic() + 
  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5),
        strip.background = element_blank(),
        legend.position = "right",
        strip.text.x = element_text(size = 10, angle = 0, face="bold"),
  ) + 
  #geom_point(aes(shape = C.section..Yes.No.), size = 3) +
  scale_x_reverse() +# Revert x-axis to match plots
  #ggtitle("Time point")+
  facet_wrap("Sample_time_point")
#ggplot2::annotate("text", x = -0.3, y = 0.3, label = "P < 0.001") #Add p-value from adonis

beta.treatment
```
```
# Abundance heatmaps
## Bacteria  - Treatment

```{r, eval = T, include = T, echo = F, message = F, warning =  F, fig.width=10, fig.height=4, fig.fullwidth = TRUE}
#Load phyloseq files to ampvis2 format

PSBamp <- phyloseq_to_ampvis2(PSB)  

#Bacteriome

amp_heatmap(PSBamp,
            group_by = "Treatment",
            facet_by = "Sample_time_point",
            plot_values = FALSE,
            tax_show = 20,
            tax_aggregate = "Genus" ,
            #tax_add = "Family",
            tax_empty = "best",
            normalise = TRUE,
            color_vector = c("white", "red"),
            plot_colorscale = "sqrt",
            plot_legendbreaks = c(1, 10, 25, 50)
) +
  theme_classic() +
  theme(strip.background = element_rect(colour = "black", fill = "white"),
        strip.text.x = element_text(face = "bold"),
        axis.text.x=element_text(angle = -45, hjust = 0,vjust = 0.2))
```

